### 2021-04-08 Chapter-6/Chapter-6.tex
Updates from Overleaf

\chapter{Future Work and Conclusion}\label{chapter6}

>>>>

\chapter{Conclusion and Future Work}\label{chapter6}
This dissertation research studies the address-based side-channel leakages in two aspects: detection and quantification. In the side-channel vulnerability detection research, we explore and solve the two bottlenecks in today's automated side-channel vulnerability detection tool, performance and precision. In the side-channel vulnerability quantification research, we propose two different side-channel leakage quantification tools based on information theory.

In Chapter~\ref{chapter3}, we present the first technique \detect{}.
